Consistency scores in text data

### 2020-07-14 outputs/documents/paper.Rmd
n-gram parts revision

The probability of a sequence appearing in a corpus follows the chain rules:

@@

This will soon grow weary if the sentences are long. Instead, the Markov assumption permits us to approximate the probability using only the last $n$ words. More specifically:

@@

Simplified and formalized to:

> P($w^{n}_{1}) \approx$ P($w_{1}$) $\cdot$ P($w_{2} | w_{1}$) ... P($w_{n} | w_{n-1}$)

The application of n-gram is versatile. N-gram is widely applied in text prediction, spelling-correction, machine translation...

>>>>

To predict a word appearing next, we have to take the sequence of preceeding words into account, which requires knowing the probability of the sequence of words. The probability of a sequence appearing in a corpus follows the chain rules:

@@

However, the likelihood that more and more words will occur next to each other in an indentical sequence becomes smaller and smaller, making the prediction difficult. Instead, the Markov assumption permits us to approximate the probability using only the last $n$ words **(Keli add citation)**. More specifically

@@

Because the bigram model looks into one word in the past, the n-gram under Markov assumption can then be generalized into a bigram model with n being any number. The general equation is

P($w_{n} | w^{n-1}_{1}) \approx$ P($w_{n} | w^{n-1}_{n - N+1})$)

The application of n-gram is versatile. N-gram is widely applied in text prediction, spelling-correction, machine translation. We use n-gram to [add how we use n-gram once the functions in the app are in place]
